A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
Fix typos in I and II

The origins of \eval go back to the first implementation of the Lisp
programming language~\cite{lisp}. Over the years, \eval has been included in
many dynamic languages, with some variability in expressive power and
nomenclature. In all of its incarnation \eval allow developpers to
dynamically extend the code of their program at run-time.  Originally, \eval
was limited to interpreted languages, but with the advent of just-in-time
compilation this restriction was gradually lifted.

Some languages have chosen to restrict \eval. The essential difference
between languages relates to scoping of variables that can be accessed from
code executed by \eval.  Java and Julia are among the more restrictive
languages. In Java, \eval must be synthesized as a combination dynamic
loading and reflection.\footnote{While Java does not have \eval built-in,
  one can take the input to \eval, wrap it in a static method of an
  anonymous class, generate bytecode for that class, invoke the Java class
  loader to dynamically install the new code, and then use reflection to
  call the new method.} Julia provides \eval more directly but limits its
scope to top level variables and methods. JavaScript support both a,
so-called, global \eval, and a local \eval. Where the latter has acces to
local variables of the function being executed (as well as variables of
lexically enclosing scopes). Finally languages such as R allow \eval to
manipulate variables defined in the caller environment of the function in
which \eval is invoked.

@@

Wang et al.~\cite{wang} analyzed usage of dynamic features in 18 Python
programs include dynamic code generation to find if they affects file
change-proneness.  They reported that files with dynamic features are
significantly more likely to be the subject of changes, than other files.
Chen et al. looked at the correlation between code changes and dynamic
features, including \eval, in 17 Python programs~\cite{chen}. They did not
observe many uses of \eval.  Callau et al. performed an empirical study of
the usage of dynamic features in the 1,000 largest Smalltalk projects in the
Squeaksource repository, accounting for more than 4 million lines of
code~\cite{oscar}. While \eval itself is not present, Smalltalk has a rich
reflective interface that gives programmer great flexibility. Their work was
based on a static analysis.

Morandat et al.~\cite{ecoop12} had a short section on the usage of \eval in
R. They found the \eval function to be widely used in R code with 8500 call
sites in CRAN and 2.2 million dynamic calls. The 15 most frequent call sites
account for 88\% of eval. The \c{match.arg} function is the highest user
with 54\% of all calls. In the other call sites, they saw two uses
cases. The most common is the evaluation of the source code of a promise
retrieved by \c{substitute} in a new environment. This is done in the
\c{with} function. The other use case is the invocation of a function whose
name or arguments are determined dynamically. For this purpose, R provides
\c{do.call} and thus using \eval is overkill.

>>>>

The origins of \eval go back to the first implementation of the Lisp
programming language~\cite{lisp}. Over the years, \eval has been included in
many dynamic languages, with some variability in expressive power and
nomenclature. In all of its incarnation \eval allows developers to
dynamically extend the code of their program at run-time.  Originally, \eval
was limited to interpreted languages, but with the advent of just-in-time
compilation this restriction was gradually lifted.

Some languages have chosen to restrict \eval. The essential difference
between languages relates to scoping of variables that can be accessed from
code executed by \eval.  Java and Julia are among the more restrictive
languages. In Java, \eval must be synthesized as a combination of dynamic
loading and reflection.\footnote{While Java does not have \eval built-in,
  one can take the input to \eval, wrap it in a static method of an
  anonymous class, generate bytecode for that class, invoke the Java class
  loader to dynamically install the new code, and then use reflection to
  call the new method.} Julia provides \eval more directly but limits its
scope to top level variables and methods. JavaScript support both a,
so-called, global \eval, and a local \eval. Where the latter has acces to
local variables of the function being executed (as well as variables of
lexically enclosing scopes). Finally languages such as R allow \eval to
manipulate variables defined in the caller environment of the function in
which \eval is invoked.

@@

Wang et al.~\cite{wang} analyzed usage of dynamic features in 18 Python
programs include dynamic code generation to find if they affect file
change-proneness.  They reported that files with dynamic features are
significantly more likely to be the subject of changes, than other files.
Chen et al. looked at the correlation between code changes and dynamic
features, including \eval, in 17 Python programs~\cite{chen}. They did not
observe many uses of \eval.  Callau et al. performed an empirical study of
the usage of dynamic features in the 1,000 largest Smalltalk projects in the
Squeaksource repository, accounting for more than 4 million lines of
code~\cite{oscar}. While \eval itself is not present, Smalltalk has a rich
reflective interface that gives programmer great flexibility. Their work was
based on a static analysis.

Morandat et al.~\cite{ecoop12} had a short section on the usage of \eval in
R. They found the \eval function to be widely used in R code with 8500 call
sites in CRAN and 2.2 million dynamic calls. The 15 most frequent call sites
account for 88\% of eval. The \c{match.arg} function is the highest used one
with 54\% of all calls. In the other call sites, they saw two uses
cases. The most common is the evaluation of the source code of a promise
retrieved by \c{substitute} in a new environment. This is done in the
\c{with} function. The other use case is the invocation of a function whose
name or arguments are determined dynamically. For this purpose, R provides
\c{do.call} and thus using \eval is overkill.
